Residence time, a master variable of ecology, physiology, and natural selection

### 2015-09-10 analyses/ForPaper/MultivariateTests.Rmd

>>>>

```{r, results='hide', echo=F, message=F, warning=F, fig.width=7, fig.height=4}
Nfit <- lm(log(sim.data$total.abundance) ~ h.tau)
summary(Nfit)

Sfit <- lm(log(sim.data$species.richness) ~ h.tau)
summary(Sfit)

Efit <- lm(sim.data$simpson.e ~ h.tau)
summary(Efit)

Bfit <- lm(sim.data$species.turnover ~ h.tau)
summary(Bfit)

x <- sim.data$total.abundance

Nfit <- lm(log(sim.data$total.abundance) ~ x)
summary(Nfit)

Sfit <- lm(log(sim.data$species.richness) ~ x)
summary(Sfit)

Efit <- lm(sim.data$simpson.e ~ x)
summary(Efit)

Bfit <- lm(sim.data$species.turnover ~ x)
summary(Bfit)
```
